---
title: "Data Sources"
author: "JJC"
format: html
editor: visual
---

```{r}
#| label: load libraries
#| include: false

library(data.table)
library(readxl)
library(janitor)
library(tidyr)
library(gt)
```

## Population

### **2011 Ireland Census -** Central Statistics Office

External html script: [CSO - Population by year of age, 2011](https://data.cso.ie/table/CD205)

Run the R chunk below and select "Download CSV" to the *raw-data* folder. Enter the file name: *CD205-Pop-2016* The file type is csv.

```{r}
#| eval: false

library(htmltools)
htmltools::includeHTML("./scripts/CD205-Pop-2011.html")
```

### **2016 Ireland Census -** Central Statistics Office

[CSO - Population by year of age, 2016](https://data.cso.ie/table/CNA20)

Run the R chunk below and select "Download CSV" to the *raw-data* folder. Enter the file name: *CNA20-Pop-2016* The file type is csv.

```{r}
#| eval: false

library(htmltools)
htmltools::includeHTML("./scripts/CNA20-Pop-2016.html")
```

### **2022 Ireland Census -** Central Statistics Office

[CSO - Population by year of age, 2022](https://data.cso.ie/table/FY006B)

Run the R chunk below and select "Download CSV" to the *raw-data* folder. Enter the file name: *FY006B-Pop-2022* The file type is csv.

```{r}
#| eval: false

library(htmltools)
htmltools::includeHTML("./scripts/FY006B-Pop-2022.html")
```

### Population Estimates, 2023

Run the html script below and download file to *./raw-data/PEA01-Pop-Est-2023.csv*

```{r}
#| eval: false

library(htmltools)
htmltools::includeHTML("./scripts/PEA01-Pop-Est-2023.html")
```

### Population Estimates, 2015-2021

[CSO Table PEA01 Population Estimates](https://data.cso.ie/table/PEA01)

To download data file, click link below

[Estimated Population classified by Sex and Age Group, 2015 - 2021](https://www.cso.ie/en/media/csoie/releasespublications/documents/ep/populationandmigrationestimates/2021/P-PME2021TBL1.8.xlsx)

and save the file to the *raw-data* folder. Enter the file name: *PEA01-Pop-Est*\
The file type is xlsx.

### Population Estimates, 2010-2014

Run the html script below and download file to *./raw-data/PEA01-Pop-Est-2010-2014.csv*

```{r}
#| eval: false

library(htmltools)
htmltools::includeHTML("./scripts/PEA01-Pop-Est-2010-2014.html")
```

## Mortality

[CSO - Mortality by Age Group and Quarter Year](https://data.cso.ie/table/VSAQ2)

Run the R chunk below and select "Download CSV" to the *raw-data* folder. Enter the file name: *VSAQ2-Mort-Age-2010-2023* The file type is automatically set to csv.

```{r}
#| eval: false

library(htmltools)
htmltools::includeHTML("./scripts/VSAQ2-Mort-Age-2010-2023.html")
```

Go to [EuroStat demo_magec dataset](https://ec.europa.eu/eurostat/databrowser/view/demo_magec__custom_9481166/default/table?lang=en "custom query to EuroStat")

Select `Download` \>\
\> `Data on this page only`\
\> `Spreadsheet (.xlsx)`

and save file in `raw-data` folder

\

## Vaccinations

### 
