---
title: "Data Sources"
author: "JJC"
format: html
editor: visual
---

```{r}
#| label: load libraries
#| include: false

library(data.table)
library(readxl)
library(janitor)
library(tidyr)
library(gt)
```

## Population

### **2011 Ireland Census -** Central Statistics Office

External html script: [CSO - Population by year of age, 2011](https://data.cso.ie/table/CD205)

Run the R chunk below and select "Download CSV" to the *raw-data* folder. Enter the file name: *CD205-Pop-2016* The file type is csv.

```{r}
#| eval: false

library(htmltools)
htmltools::includeHTML("./scripts/CD205-Pop-2011.html")
```

### **2016 Ireland Census -** Central Statistics Office

[CSO - Population by year of age, 2016](https://data.cso.ie/table/CNA20)

Run the R chunk below and select "Download CSV" to the *raw-data* folder. Enter the file name: *CNA20-Pop-2016* The file type is csv.

```{r}
#| eval: false

library(htmltools)
htmltools::includeHTML("./scripts/CNA20-Pop-2016.html")
```

### **2022 Ireland Census -** Central Statistics Office

[CSO - Population by year of age, 2022](https://data.cso.ie/table/FY006B)

Run the R chunk below and select "Download CSV" to the *raw-data* folder. Enter the file name: *FY006B-Pop-2022* The file type is csv.

```{r}
#| eval: false

library(htmltools)
htmltools::includeHTML("./scripts/FY006B-Pop-2022.html")
```

### Population Estimates

Annual estimates of the population are contained in [CSO Table PEA01 Population Estimates](https://data.cso.ie/table/PEA01)

Select the years 2010, 2012-2015, 2017-2021, and 2023. Also, select for all age groups and both sexes. Download the CSV file to *./raw-data/PEA01-Estimates.csv*

## Mortality

[CSO - Mortality by Age Group and Quarter Year](https://data.cso.ie/table/VSAQ2)

Run the R chunk below and select "Download CSV" to the *raw-data* folder. Enter the file name: *VSAQ2-Mort-Age-2010-2023* The file type is automatically set to csv.

```{r}
#| eval: false

library(htmltools)
htmltools::includeHTML("./scripts/VSAQ2-Mort-Age-2010-2023.html")
```

### EuroStat

Go to [EuroStat demo_magec dataset](https://ec.europa.eu/eurostat/databrowser/view/demo_magec__custom_9481166/default/table?lang=en "custom query to EuroStat")

Select `Download` \>\
\> `Data on this page only`\
\> `Spreadsheet (.xlsx)`

and save file in `raw-data` folder

## Vaccinations

#### CSO

The Central Statistics Office covers each 166 electoral areas in Ireland and does not give total over all areas. In addition, vaccinations administered are recorded as a percent of area population. By not giving total numbers vaccinated in an area, it makes it difficult to calculate total overall counts for any given month (between 2021 and 2023).

[CSO COVID-19 Vaccination Rates](https://data.cso.ie/table/CDC47)

#### EuroStat

This analysis uses data from the COVID-19 Vaccine Tracker. This covers all weeks from w53,, 2020 up to 05 October, 2023 and includes all age groups. It records the median cumulative uptake (%) of the primary course by age group. The latest data recorded refers to a period until 5 October 2023 and no further updates have been included.

The main "Data on COVID-19 vaccination in the EU/EEA" data-set only covers doses administered during the most recent weeks.

[European Centre for Disease Prevention and Control COVID-19 Vaccine Tracker](https://vaccinetracker.ecdc.europa.eu/public/extensions/COVID-19/vaccine-tracker.html#age-group-tab)

Select Country \> Ireland\
Select Indicator \> Uptake primary course\
Select Age Groups tab in top menu

Chart: Cumulative uptake of primary course by age group\
Select Download icon from menu on right of chart

Save data in `raw-data` folder

### 
